---
title: "5.9 Implicit Points, N=360"
author: "Ben Morris and Dan Yurovsky"
date: "`r Sys.Date()`"
output:
  html_document:
    highlight: tango
    theme: flatly
    toc: true
    toc_float:
      collapsed: true
    code_folding: hide
---


These data were on MTurk collected on May 9th, 2017. 360 participants were run, with 40 in each of 9 conditions (3 pointer speeds [slow, slower, slowest] and 3 levels of partner exposure [none, 1/2 as much as you, and twice as much as you]). 

This version of the game used a pointer that moves at different speeds to manipulate the relative cost between pointing and labeling. A per-trial-timer was used to determine how many points were won, in an attempt to make the time-cost more salient and consequential, scaled to 100. Participants that the 'doing both' strategy would allow them to teach their partner. The timer begins running when a key was pressed to make labeling even less costly relative to pointing (and thus incentivize teaching). This version had the standard game structure all 9 objects shown 3 times. 


```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.align='center', messages=FALSE, warning = FALSE,
                      fig.height = 3, fig.width=5)
```

```{r load_libraries, include = FALSE, results = "hide"}
library(lme4)
library(jsonlite)
library(dplyr)
library(ggplot2)
library(tidyr)
library(lubridate)
library(langcog)
library(knitr)

novelWords <- as.vector(c("blicket", "kreeb", "wug", "fep", 
                          "toma", "dax", "gazzer", "kiv","manu"))

theme_set(theme_bw(base_size = 14) + theme(panel.grid = element_blank(),
                  strip.background = element_blank()))

# setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
```

# Load Data

```{r read_data, warning = FALSE}
filenames <- list.files("production-results/", 
                         pattern="*.json", full.names = TRUE)
filenames_5.10 <-  list.files("5.10_production-results/", pattern="*.json", full.names = TRUE)
filenames <- append(filenames, filenames_5.10)

ldf <- lapply(filenames, fromJSON)
res <- lapply(ldf, summary)

sender_timing <- NULL
sender_exposures <- NULL
sender_ruleCheck <- NULL
sender_manipulation <- NULL
sender_game <- NULL
sender_test<- NULL
sender_attn <- NULL
sender_turkIds<-NULL
sender_comments<- NULL
for (i in 1:length(ldf)) {
  janeDoe <- ldf[[i]]
  anyAttn <- ifelse(length(janeDoe$answers$data$attnCheck)!=0, 1,0)
  # else {condition <- "80_50"}
  ldf_num <- i
  sender_timing <- rbind(sender_timing, as.data.frame(
      cbind(ldf_num, start= janeDoe$AcceptTime,stop = janeDoe$SubmitTime)))
  sender_exposures <- rbind(sender_exposures, janeDoe$answers$data$expDuration)
  sender_ruleCheck <- rbind(sender_ruleCheck, janeDoe$answers$data$ruleQuestions)
  sender_manipulation <- rbind(sender_manipulation, cbind(ldf_num,janeDoe$answers$data$manipCheck))
  sender_test <- rbind(sender_test,cbind(ldf_num, janeDoe$answers$data$testTrials))
  sender_game <- rbind(sender_game,cbind(ldf_num,janeDoe$answers$data$gameTrials))
  if (length(janeDoe$answers$data$attnCheck)!=0) 
    {sender_attn <- rbind(sender_attn, janeDoe$answers$data$attnCheck)}
  sender_turkIds <- rbind(sender_turkIds, cbind(ldf_num, janeDoe$WorkerId))
  sender_comments <- rbind(sender_comments,janeDoe$answers$data$comments)
}
```

## Process and Clean the Sender Data

```{r clean_data, warning = FALSE, message=FALSE}
#join in knowledge at Test
sender_test_slim <- sender_test %>% 
  mutate(subID =as.numeric(subID)) %>%
  mutate(responseCorrect = ifelse(realLabel==adjLabel, 1, responseCorrect)) %>%
  select(targetObjectName, realLabel, subID, exposureRate, responseCorrect, ldf_num) %>%
  rename(testCorrect= responseCorrect)
#sender_game
all_data_fixed <- sender_game  %>%
  left_join(sender_test_slim %>% mutate(ldf_num = as.integer(ldf_num), subID = as.character(subID)))

all_data <- all_data_fixed %>%
  mutate(trialnum = trialnum - 36) %>%
  mutate(partnersExposure = factor(partnersExposure, levels = c("0", "1/2", "1", "perfect"),
                                   labels = c("None", "Half", "Same", 'Perfect'))) %>%
  mutate(toBeDropped=0)
```

We keep track of any participants who close or refresh the page, because any participants who did so before eventually submitting data may have had an a greater number of exposures than others and also have likely been exposed to multiple sets of object-word pairings. 

```{r clean_data, warning = FALSE, message=FALSE}
#check who closed or reloaded page against who submitted data!!
sender_turkIds_clean <- data.frame(sender_turkIds)

tmp1 <- read.table(textConnection(gsub(";","\n", readLines("experiment_files/participants_who_closed.txt"))))
tmp2 <- read.table(textConnection(gsub(";","\n", readLines("5.10_experiment_files/participants_who_closed.txt"))))

tmp <- rbind(tmp1, tmp2)
tmp <- read.table(textConnection(gsub(","," ", tmp$V1)))

quit_participants <- tmp %>% 
  filter(V1 %in% sender_turkIds_clean$V2) %>%
  left_join(sender_turkIds_clean, by=c("V1" = "V2"))
quit_participants$V2 <- as.numeric((quit_participants$V2))
quitters <- quit_participants[which(quit_participants$V2 > 1),]


all_data <- all_data %>%
  mutate(toBeDropped = ifelse(ldf_num %in% quitters$ldf_num, 1, toBeDropped)) 
```


Also drop people who fail manipulation check.  
```{r clean_data, warning = FALSE, message=FALSE}
#people who pass manipulation check
manipFail <- (sender_manipulation %>% filter(manipCorrect==0) %>% select(ldf_num))

all_data <- all_data %>%
  mutate(toBeDropped = ifelse(ldf_num %in% manipFail$ldf_num, 1, toBeDropped))
```


Also drop people who submit nonsense messages. 
```{r clean_data, warning = FALSE, message=FALSE}
#also check for wonky repsonse
# e.g. ldf_num 26?
how_many_adj <- sender_game %>% 
  ungroup() %>%
  mutate(adjusted = if_else(is.na(typedLabel), as.numeric(NA), 
                            if_else(typedLabel %in% novelWords, 0, 1))) %>%
  # mutate(adjusted = ifelse(typedLabel != adjLabel, 1, 0)) %>%
  group_by(ldf_num) %>%
  summarize(n_Adjusts = sum(adjusted, na.rm=TRUE), num_Corr = sum(responseCorrect, na.rm=TRUE))

hist(how_many_adj$n_Adjusts, breaks= 27)
nrow(how_many_adj  %>% filter(n_Adjusts>18))
quantile(how_many_adj$n_Adjusts, prob=.95)
way_off_subjs <- how_many_adj %>%
  filter(n_Adjusts > 18)

way_off_trials <- sender_game %>% filter(ldf_num %in% way_off_subjs$ldf_num) %>% 
  select(ldf_num, typedLabel, adjLabel, realLabel)  %>%
  filter(typedLabel != adjLabel)

all_data <- all_data %>%
  mutate(toBeDropped = ifelse(ldf_num %in% way_off_subjs$ldf_num, 1, toBeDropped))
```


####Check for runs of strings that are repated as messages.

  In these data there are 5 participants who sent messages 3 or more times in a row.  
```{r clean_data, warning = FALSE, message=FALSE}
# same string three times in a row?
findRuns <- function(word, count) {
  runs <- ifelse(word == lag(word), findRuns(lag(word), count+1), count)
  ifelse(is.na(runs), 0, runs)
}

send_freqs <- filter(sender_game) %>%
  arrange(partnersExposure,ldf_num,trialnum) %>%
  group_by(ldf_num) %>%
  mutate(n_back = findRuns(typedLabel, 0)) %>%
  group_by(partnersExposure, ldf_num, typedLabel) %>%
  summarise(n_back = max(n_back)) %>%
  filter(!is.na(typedLabel))

n_back_subjs <- send_freqs %>%
  #note that n_back == 2 is a 3-string run
  filter(n_back >= 2) %>%
  select(ldf_num)

all_data <- all_data %>%
  mutate(toBeDropped = ifelse(ldf_num %in% n_back_subjs$ldf_num, 1, toBeDropped))

```

####Check for participants who sent the same message many times over all trials

  Drop participants who send the same label 6 or more times across all the game trials. This places them outside of 97.5% confidence intervals and thus their data is excluded from further analyses. 
```{r clean_data, warning = FALSE, message=FALSE}
  # same message just >=6 times total?

repeated_words <-  sender_game %>%
  filter(method != "click") %>%
  group_by(ldf_num, typedLabel, realLabel) %>%
  summarise(n = n()) %>%
  group_by(ldf_num, typedLabel) %>%
  summarize(n=sum(n), num_targets= n()) %>% 
  group_by(ldf_num) %>%
  summarise(n = max(n))


repeated_words_subjs <- repeated_words %>%
  filter(n >= 6) 

all_data <- all_data %>%
  mutate(toBeDropped = ifelse(ldf_num %in% repeated_words_subjs$ldf_num, 1, toBeDropped))

```



####Check for single character messages
```{r clean_data, warning = FALSE, message=FALSE}
charLength <- sender_game %>% 
  mutate(typedChar = nchar(typedLabel)) %>%
  select(ldf_num, typedLabel, typedChar) 

one_letter_subjs <- charLength %>%
  filter(typedChar==1) %>%
  group_by(ldf_num) %>%
  summarize(n=n()) %>%
  filter(n > 1)

all_data <- all_data %>%
  mutate(toBeDropped = ifelse(ldf_num %in% one_letter_subjs$ldf_num, 1, toBeDropped))
```

####Check for English

  After doing the above exclusions, an experimenter manually checked all remaining messages where the label was not part of the starting lexicon. While the game program checks participants messages to prevent english labels from being used during the game, some particpants produced pseud-english labels which skirted this rule. In the manual check, any participant who produced a pseudo-english label (e.g., 'blu') was removed from analyses. 
  
  Additionally, any participant who produced a nonsense label (e.g., 'xdhi') that was not caught by the above rules was also removed. 
```{r clean_data, warning = FALSE, message=FALSE}
# do all the filtering, then check any typedLabels that got through for english words.
all_data_dropped <- all_data %>%
  filter(toBeDropped == 0)

non_vocab_labels <- all_data_dropped %>%
  filter(!is.na(typedLabel)) %>%
  filter(!typedLabel %in% novelWords)
# non_vocab_labels %>% select(ldf_num,typedLabel, realLabel) %>% View()

english_subjs <- c(30, 39, 159, 228, 253, 296)
nonsense_subjs <- c(133, 187, 242, 396)
borderline <- c(142, 162, 258, 275, 309)

all_data <- all_data %>%
  mutate(toBeDropped = ifelse(ldf_num %in% english_subjs, 1, toBeDropped)) %>%
  mutate(toBeDropped = ifelse(ldf_num %in% nonsense_subjs, 1, toBeDropped))
```


####Also check for condition assignment inquealities. 

   After filtering out the bad data, we also need to account for the bug in condition assignment on May 9th that caused too many pariticpants to be run in one condition. We will keep only the first 40 pariticpants that submitted usable data for that condition, and exclude the remaining from subsequent analyses. 
```{r clean_data, warning = FALSE, message=FALSE}
### check for doubling...
  ### check the condition assignment bug...
sender_game %>% 
  distinct(ldf_num, username, speed, partnersExposure) %>% 
  group_by(speed, partnersExposure) %>%
  summarize(n=n()) 
# error where one condition received double the pariticpants, need to drop folks

## after dropping
all_data %>% 
  filter(toBeDropped==0) %>% 
  distinct(ldf_num, username, speed, partnersExposure) %>% 
  group_by(speed, partnersExposure) %>%
  summarize(n=n()) 

assignment_bug <- all_data %>% 
  filter(toBeDropped==0, partnersExposure=="Half", speed=="30") %>%
  left_join(sender_timing %>% mutate(ldf_num=as.numeric(ldf_num))) %>%
  distinct(ldf_num, stop) %>%
  mutate(stop = ymd_hms(stop)) %>%
  arrange(stop)

extra_subjs_bug <- assignment_bug[41:nrow(assignment_bug),]

all_data <- all_data %>%
  mutate(toBeDropped = ifelse(ldf_num %in% extra_subjs_bug$ldf_num, 1, toBeDropped))


all_data %>% 
  filter(toBeDropped==0) %>% 
  distinct(ldf_num, username, speed, partnersExposure) %>% 
  group_by(speed, partnersExposure) %>%
  summarize(n=n()) 
```


```{r by_appearance, include=FALSE}

all_data_dropped <- all_data %>%
  mutate(speed = as.factor(speed)) %>%
  filter(toBeDropped != 1)  %>%
  group_by(ldf_num, exposureRate, targetObjectName) %>%
  mutate(appearance = if_else(trialnum == min(trialnum), "First",
                              if_else(trialnum == max(trialnum), "Third", "Second")))

```




# Analysis


### Test Performance

As we have shown in previous versions, recall of object-label mappings scales sensibly with exposure.
```{r test_results, fig.height=5, fig.width=4, message=FALSE}

seprop <- function(props) {
  mean_prop = mean(props)
  sqrt( (mean_prop*(1 - mean_prop)) / length(props))
}

# quartz(width = 6, height = 7)
sender_test %>%
  filter(ldf_num %in% all_data_dropped$ldf_num) %>%
  mutate(testCorrect=ifelse(typedLabel=='UNKNOWN', "Unknown", 
                            as.character(responseCorrect))) %>%
  group_by(exposureRate, ldf_num) %>%
  mutate(testCorrect = ifelse(typedLabel==adjLabel, "1", testCorrect)) %>%
  summarise(performance = mean(testCorrect=="1")) %>%
  summarize_each(funs(mean, seprop), performance) %>%
  ggplot(aes(x = as.factor(exposureRate), y = mean)) +
    geom_bar(stat = "identity", position="dodge", fill="#e41a1c") +
    geom_linerange(aes(ymax = mean + seprop, 
                      ymin = mean - seprop), position=position_dodge(.9)) + 
    labs(x="Exposure Rate", y="Proportion Correct") +
    # scale_fill_discrete(name='Condition', labels=c("Talk is Cheap", "Talk is Expensive")) +
    coord_cartesian(ylim=c(0,1))
```


### Message Strategy Across Condtions As a Function of Appearance


```{r}
gm_label <- glmer((method=='label') ~ appearance +
                partnersExposure +
                speed +
                exposureRate +
               (1|ldf_num),
            data=all_data_dropped,
      family=binomial)

gm_teach <- glmer((method=='label_click') ~ appearance +
                partnersExposure +
                speed +
                exposureRate +
               (1|ldf_num), 
            data=all_data_dropped,family=binomial)

gm_click <- glmer((method=='click') ~ appearance +
                partnersExposure +
                speed +
                exposureRate +
               (1|ldf_num),
            data=all_data_dropped,family=binomial)
```



```{r by_appearance, warning=FALSE, message=FALSE, fig.width=3, fig.height=4}

prop_methods <- all_data_dropped %>%
  filter(toBeDropped != 1) %>%
  group_by(partnersExposure,speed, ldf_num, appearance, method) %>%
  summarise(n = n()) %>%
  group_by(partnersExposure, speed, appearance, ldf_num) %>%
  mutate(n = n/sum(n)) %>%
  mutate(method = as.factor(method)) %>%
  complete(appearance, method, ldf_num, fill = list(n = 0)) %>%
  group_by(partnersExposure,speed, appearance, method) %>%
  summarise(n = mean(n)) %>%
  mutate(method = factor(method, levels = c("click", "label", "label_click")))
  
  
  # group_by(ldf_numpartnersExposure, speed, appearance, method, ) %>%
  # summarise(n = n()) %>% 
  # complete(appearance, method, ldf_num, fill = list(n = 0)) %>%
  # summarise(n = mean(n)) %>%
  # mutate(n = n/sum(n))
  

# all_methods <- expand.grid(partnersExposure = unique(prop_methods$partnersExposure), 
                             # appearance = unique(prop_methods$appearance), 
                            # method = unique(prop_methods$method))

prop_methods %>%
  ggplot(aes(x=appearance, y=n,  fill=method)) +
       geom_bar(stat = "identity", position="stack", width = .70) +
  facet_grid(partnersExposure ~ speed) +
  labs(y="Proportion of Trials", x="Appearance #") +
  scale_fill_brewer(name = "Message Type", 
                    labels=c("Click", "Label", "Teach"),
                    palette = "Set1")

ggplot(prop_methods, aes(x = appearance, y = n, color = method,
                group = interaction( method))) + 
  facet_grid(partnersExposure ~ speed) +
  geom_line()

```


### Participants who teach
```{r, echo=FALSE}
teach_subs <- all_data_dropped %>%
  group_by(ldf_num, partnersExposure, speed) %>%
  summarise(teach_freq = sum(method == "label_click"))

ggplot(teach_subs, x=teach_freq) + 
  geom_histogram(aes(x=teach_freq), bins=27) + 
  facet_grid(partnersExposure~speed)
  
teach_subs %>% group_by(speed, partnersExposure) %>% summarize(nTeachers= n(), avgTeach=mean(teach_freq))

kable(teach_subs)
```

```{r, echo=FALSE}
tmp <- all_data_dropped %>%
  filter(speed == 20) %>%
  group_by(ldf_num, realLabel) %>%
  mutate(partnersExposure = factor(partnersExposure, levels = c("Perfect", "Half", "None"))) %>%
  mutate(appearance = if_else(trialnum == min(trialnum), "First",
                              if_else(trialnum == max(trialnum), "Third", "Second"))) %>%
  group_by(partnersExposure,ldf_num, appearance, exposureRate, method) %>%
  summarise(n = n()) %>%
  group_by(partnersExposure,appearance, exposureRate, ldf_num) %>%
  mutate(n = n/sum(n)) %>%
  mutate(method = as.factor(method)) %>%
  complete(appearance, exposureRate, method, ldf_num, fill = list(n = 0)) %>%
  group_by(partnersExposure,appearance, exposureRate, method) %>%
  summarise(n = mean(n))
  
  
ggplot(tmp, aes(x = appearance, y = n, color = method,
                group = interaction( method))) + 
  facet_grid(partnersExposure ~ exposureRate) +
  geom_line()
  
  
  #   arrange(ldf_num, appearance, exposureRate, method) %>%
  # summarise(teach_freq = sum(method == "label_click"))


  
ggplot(teach_subs, x=teach_freq) + 
  geom_histogram(aes(x=teach_freq), bins=27) + 
  facet_grid(partnersExposure~speed)
  
teach_subs %>% group_by(speed, partnersExposure) %>% summarize(nTeachers= n(), avgTeach=mean(teach_freq))

kable(teach_subs)
```

```{r label_prop, fig.height=5, fig.width=4}
label_props <- all_data_dropped %>%
  group_by(partnersExposure, 
           exposureRate,
           subID) %>%
  summarise(empirical = mean(method == "label")) %>%
  summarize_each(funs(mean, seprop),empirical) 

### Bar Plot of Proportion of Trials where Labels Are Sent, by Condition (empirical results)
# quartz(width = 10, height = 7)
label_props %>% 
  ggplot( aes(x = as.factor(exposureRate), y = mean, 
             fill = partnersExposure)) +
   geom_bar(stat = "identity", position="dodge") +
  geom_linerange(aes(ymax = mean + seprop, 
                      ymin = mean - seprop), position=position_dodge(.9)) + 
  labs(x="Exposure Rate", y="Proportion of Labelling Behavior", 
       title="Propensity to Send Labels During the Game") +
  scale_fill_brewer(name="Partner's Exposure", palette = "Set1") +
  coord_cartesian(ylim=c(0,1))


```






### Duration by Method (ish)

Note this is an imperfect reflection of the scores. 
```{r, message=FALSE}
all_data %>% group_by(method) %>%
  # filter(duration<15000) %>%
  summarize(medDur = median(duration), sdDur = sd(duration), n =n(), avgCorr = mean(responseCorrect)) %>%
  kable()

```

### Participant Info, Comments, Etc
```{r, message=FALSE}

test_performance <- sender_test %>%
  mutate(responseCorrect = ifelse(realLabel==adjLabel, 1, responseCorrect)) %>%
  group_by(exposureRate) %>%
  mutate(responseCorrect = ifelse(responseCorrect== "UNKNOWN", 0, as.numeric(responseCorrect))) %>%
  summarize(meanDur = mean(duration), avgCorr = mean(responseCorrect), sdCorr = sd(responseCorrect))


tmp <- sender_test %>%
  mutate(testCorrect=ifelse(typedLabel=='UNKNOWN', "Unknown", 
                            as.character(responseCorrect))) %>%
  group_by( ldf_num) %>%
  mutate(testCorrect = ifelse(typedLabel==adjLabel, "1", testCorrect)) %>%
  summarise(performance = mean(testCorrect=="1"))  %>%
  left_join(sender_comments) %>%
  arrange(performance) %>%
  left_join(teach_subs) %>%
  left_join(sender_manipulation, by='ldf_num') %>%
  select(ldf_num, performance, enjoyedGame, teachingQuestion, teach_freq, comments, manipResponse, manipCorrect)

kable(tmp)
```