---
title             : "Communicative pressure on caregivers leads to language input that supports children's word learning"
shorttitle        : "Learning form communicative input"

author: 
  - name          : "Benjamin C. Morris"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Department of Psychology, University of Chicago, 5848 S University Ave, Chicago, IL 60637"
    email         : "benmorris@uchicago.edu"
  - name          : "Daniel Yurovsky"
    affiliation   : "2"
    corresponding : no    # Define only one corresponding author

affiliation:
  - id            : "1"
    institution   : "University of Chicago"
  - id            : "2"
    institution   : "Carnegie Mellon University"

author_note: |
  All data and code for these analyses, as well as details of the preregistration are available at https://osf.io/d9gkw/.


abstract: >
  Children do not learn language from passive observation of the world, but from interaction with caregivers motivated to communicate with them. Does this communicative pressure on caregivers lead them to structure children's linguistic input in a way that facilitates learning? As a case study, we analyze a canonical pedagogical behavior in caregivers: use of ostensive labeling to teach children new words. Using a multi-method approach, we show that this pedagogically supportive behavior can emerge from communicative pressure alone, without any explicit pedagogical goals. First, in a corpus study, we show that parents communicate by ostensive labeling precisely when children are likely to learn a new word. In an iterated reference game, we experimentally show that this strategy can arise from pressure to communicate successfully with a less knowledgeable partner. Then, we show that speaker behavior in our experiment can be explained by a rational communication model that includes planning, without any explicit teaching goal. Finally, in a series of simulations, we explore the language learning consequences of having a communicatively-motivated caregiver. We show that under many parameterizations, simple learning mechanisms interacting with a communicatively-motivated partner outperform more powerful learning mechanisms. This perspective offers a first step toward a unifying, formal account of both how linguistic input is structured and how children learn from it.
  
keywords          : "communication; child-directed speech; language learning; computational modeling"
wordcount         : "X"

bibliography      : ["reference-game.bib"]

header-includes:
  - \usepackage{xcolor}

figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : yes

lang              : "english"
class             : "man"
output            : papaja::apa6_pdf
csl               : "apa7.csl"
documentclass     : "apa7"
---

```{r load-packages, warning = FALSE, message = FALSE}
library(papaja)
library(data.table)
library(feather)
library(here)
library(lme4)
library(lmerTest)
library(png)
library(boot)
library(broom)
library(broom.mixed)
library(ggthemes)
library(tidyverse)
library(tidyboot)
library(glue)
library(egg)
library(latex2exp)
library(directlabels)
library(janitor)
library(boot)

knitr::opts_chunk$set(fig.pos = 'tb', echo = FALSE, cache = TRUE, 
                      warning = FALSE, message = FALSE, 
                      sanitize = TRUE, fig.path='figs/', fig.width = 3,
                      fig.height = 3)

theme_set(theme_few(base_size = 12) + theme(legend.position = "none")) 
options(digits = 3, dplyr.summarise.inform = FALSE)
set.seed(42)
```

\newcommand{\E}[1]{\mathbb{E}\left[ #1 \right]}


```{r make-text-vars}
make_text_vars <- function(df, term_name, term_filter = NULL) {
  if(!is.null(term_filter)) {
    filtered_df <- df %>%
      filter(term == term_filter) 
  } else{
    filtered_df <- df
  }
    
  walk(c("estimate", "statistic", "p.value"), 
      ~assign(glue("{term_name}_{.x}"), 
              filtered_df %>% pull(!!.x), 
         envir = globalenv()))
}
```

One of the most striking aspects of children’s language learning is just how quickly they master the complex system of their natural language [@bloom2000]. In just a few short years, children go from complete ignorance to conversational fluency in a way that is the envy of second-language learners attempting the same feat later in life [@newport1990]. What accounts for this remarkable transition?

Distributional learning presents a unifying account of early language learning: Infants come to language acquisition with a powerful ability to learn the latent structure of language from the statistical properties of speech in their ambient environment [@saffran2003]. Distributional learning mechanisms can be seen in accounts across levels of language, including phonemic discrimination [@maye2002], word segmentation [@saffran2003], learning the meanings of both nouns [@smith2008] and verbs [@scott2012], learning the meanings of words at multiple semantic levels [@xu2007], and perhaps even the grammatical categories to which a word belongs [@mintz2003]. A number of experiments have confirmed both the early availability of distributional learning mechanisms, and their potential utility across these diverse language phenomena [@decasper1980; @decasper1986; @gomez1999; @graf2007; @maye2002; @saffran1996; @smith2008; @xu2007]. 

However, there is reason to be suspicious about just how precocious statistical learning abilities are in early development. Although these abilities are available early, they are highly constrained by limits on other developing cognitive capacities. For example, infants’ ability to track the co-occurrence information connecting words to their referents is constrained significantly by their developing memory and attention systems [@smith2013; @vlach2013]. In addition, computational models of statistical learning show that the rate of acquisition is highly sensitive to variation in environmental statistics. For example, the Zipfian distribution of word frequencies and word meanings in the real world can lead to very long learning times for rare words [@vogt2012]. Further, a great deal of empirical work demonstrates that cross-situational learning even in adults drops off rapidly when participants are asked to track more referents, and also when the number of intervening trials is increased--features likely typical of the naturalistic learning environment [e.g., @yurovsky2015]. Thus, precocious unsupervised statistical learning appears to fall short of a complete explanation for rapid early language learning.

Even relatively constrained statistical learning could be rescued, however, if caregivers structured their language in a way that simplified children's learning problem. Caregivers do adjust many aspects of their communication when conversing with young children, in both their language [infant directed speech, @snow1977] and actions [motionese, @brand2002]-and such modifications have been shown to yield learning benefits across a number of language phenomena. For example, in phoneme learning, infant-directed speech provides examples that seem to facilitate the acquisition of phonemic categories [@eaves2016]. In word segmentation tasks, infant-directed speech facilitates infant learning more than matched adult-directed speech [@thiessen2005]. In word learning scenarios, caregivers produce more speech during episodes of joint attention with young infants, which uniquely predicts later vocabulary [@tomasello1986]. Child-directed speech even seems to support learning at multiple levels in parallel--e.g., simultaneous speech segmentation and word learning [@yurovsky2012]. For each of these language problems faced by the developing learner, caregiver speech exhibits structure that seems uniquely beneficial for learning. 

Under distributional learning accounts, the existence of this kind of structure is a theory-external feature of the world that does not have an independently motivated explanation. Such accounts view the explaining the process that generates structure in the language environment as a problem separate from explaining language learning. However, across a number of language phenomena, the language environment is not merely supportive, but seems calibrated to children’s changing learning mechanisms [@yurovsky2018]. For example, across development, caregivers engage in more multimodal naming of novel objects than familiar objects, and rely on this temporal synchrony between verbal labels and gesture most with young children [@gogate2000]. The prevalence of such synchrony in child-directed speech parallels infant learning mechanisms: young infants appear to rely more on synchrony as a cue for word learning than older infants, and language input mirrors this developmental shift [@gogate2000]. Beyond age-related changes, caregiver speech may also support learning through more local calibration to a child’s knowledge. Caregivers have been shown to provide more language about referents that are unknown to their child, and adapt their language in-the-moment to the knowledge their child displays during a referential communication game [@leung2021]. The calibration of parents' production to the child's learning and knowledge suggests a co-evolution such that these processes should not be considered in isolation. 

What then gives rise to the structure in early language input that mirrors children's learning mechanisms? Because of widespread agreement that parental speech is not usually motivated by explicit pedagogical goals [@newport1977], the calibration of speech to learning mechanisms seems a happy accident; parental speech just happens to be calibrated to children's learning needs. If parental speech was pedagogically-motivated, extant formal frameworks of teaching could be used to derive predictions and expectations [e.g., @shafto2014]. This framework--in which parents choose what they say in order to maximize their children's learning--has seen some success in explaining children's developing phoneme discrimination [@eaves2016]. Even here, however, the statistical structure of phonemes in parents input also contains features that are not well explained by a pedagogical goal [@mcmurray2013].

Instead, the recent outpouring of work exploring optimal communication [the Rational Speech Act model, see @frank2012] provides a different framework for understanding parent production. Under optimal communication accounts, speakers and listeners engage in recursive reasoning to produce and interpret speech cues by making inferences over one another’s intentions [@frank2012]. These accounts have made room for advances in our understanding of a range of language phenomena previously uncaptured by formal modeling, most notably a range of pragmatic inferences [e.g., @frank2012; @goodman2016; @bohn2019]. In this work, we consider the communicative structure that emerges from an optimal communication system across a series of interactions where one partner has immature linguistic knowledge. This perspective offers the first steps toward a unifying account of both the child's learning and the parent's production: Both are driven by a pressure to communicate successfully.

Early, influential functionalist accounts of language learning focused on the importance of communicative goals [e.g., @brown1977]. Recent work has demonstrated that many structural aspects of natural language may have arisen from pressure to communicate efficiently [@gibson2019]. Our goal in this work is to formalize the intuitions in these accounts in a computational model of language input, and to test this model against experimental data. We take as the caregiver's goal the desire to communicate with the child, not about language itself, but instead about the world in front of them. To succeed, the caregiver must produce the kinds of communicative signals that the child can understand and respond contingently, potentially leading caregivers to tune the complexity of their speech as a byproduct of this in-the-moment pressure to communicate successfully [@yurovsky2018].

To examine this hypothesis, we draw on evidence from naturalistic data, a reference game experiment, a formal model, and learning simulations. We focus on ostensive labeling (i.e. using both gesture and speech in the same referential expression) as a case-study phenomenon of information-rich structure in the language learning environment.  We first analyze naturalistic parent communicative behavior in a longitudinal corpus of parent-child interaction in the home [@goldin-meadow2014]. We investigate the extent to which parents tune their ostensive labeling across their child's development to align to their child's developing linguistic knowledge [@yurovsky2016].

We then experimentally induce this form of structured language input in a simple model system: an iterated reference game in which two players earn points for communicating successfully with each other. Modeled after our corpus data, participants are asked to make choices about which communicative strategy to use (akin to modality choice). In an experiment on Mechanical Turk using this model system, we show that pedagogically-supportive input can arise from a pressure to communicate. We then show that participants' behavior in our game conforms to a model of communication as rational planning: People seek to maximize their communicative success while minimizing their communicative cost over expected future interactions. Finally, we demonstrate potential benefits for the learner through a series of simulations to show that communicative pressure on parents' speech facilitates learning. Under a variety of parameter settings, simple learners interacting with communicative partners outperform more complex statistical learners.   

In sum, our goal in this work is to argue that the fundamental unit of analysis for understanding children's language learning is not the child alone, but rather the caregiver-child dyad. To provide converging evidence for this claim, we use apply a multi-method approach to a case study of one pedagogically-supportive behavior. We use observational data to understand the contexts in which ostensive labeling happens, and then experimentally manipulate these contexts in a model system in order to demonstrate that the observed relationships are causal. We develop a formal model that quantitatively accounts for this experimental data, and then simulate the long-term learning outcomes of this model for children's language learning. Together, these different methods show that rapid language learning can emerge from even highly-constrained child learners working together with communicatively-motivated parents.

```{r child = "sections/corpus_analysis.Rmd"}
```

```{r child = "sections/experiment.Rmd"}
```

```{r child = "sections/model.Rmd"}
```

```{r child = "sections/learning_simulation.Rmd"}
```

# General Discussion

Across naturalistic corpus data, experimental data, and model predictions and simulation, we see evidence that pressure to communicate successfully with a linguistically immature partner could fundamentally structure parent production and shape child learning. In our experiment, we showed that people tune their communicative choices to varying cost and reward structures, and also critically to their partner’s linguistic knowledge-- providing richer cues when partners are unlikely to know the language and many more rounds remain. These data are consistent with the patterns shown in our corpus analysis of parent referential communication and demonstrate that such pedagogically supportive input could arise from a motivation to maximize communicative success while minimizing communicative cost–-no additional motivation to teach is necessary. In simulation, we demonstrate that simple learners whose caregivers want to communicate with them out-learn more powerful statistical learners whose caregivers do not have a communicative goal.

Accounts of language learning often aim to explain its striking speed in light of the sheer complexity of the language learning problem itself. Many such accounts argue that simple (associative) learning mechanisms alone seem insufficient to explain the rapid growth of language skills and appeal instead to additional explanatory factors, such as the so-called language acquisition device, working memory limitations, word learning biases, and many more [e.g., @chomsky1965; @goldowsky1993; @markman1990]. While some have argued for the simplifying role of language distributions [e.g., @mcmurray2007], these accounts largely focus on learner-internal explanations. For example, @elman1993 simulates language learning under two possible explanations to intractability of the language learning problem: one environmental, and one internal. He first demonstrates that learning is significantly improved if the language input data is given incrementally, rather than all-at-once. He then demonstrates that similar benefits can arise from learning under limited working memory, consistent with the "less-is-more" proposal [@elman1993; @goldowsky1993]. Elman dismisses the first account arguing that ordered input is implausible, while shifts in cognitive maturation are well-documented in the learner; our account's emphasis on calibration to such learning mechanisms suggests the role of ordered or incremental input from the environment may be crucial. Our findings support the idea that rapid language learning may be facilitated by the *combination* of the learner's limited statistical learning skills combined with communicatively (but not pedagogically) motivated caregiver input. Such results emphasize the importance of a dyadic learning approach, whereby considering the joint contributions of learner and caregiver can yield new insights [@yurovsky2018]. 

This account is consonant with work in other areas of development, such as recent demonstrations that the infant's visual learning environment has surprising consistency and incrementality, which could be a powerful tool for visual learning. Notably, research using head mounted cameras has found that infant’s visual perspective privileges certain scenes and that these scenes change across development. In early infancy, the child’s egocentric visual environment is dominated by faces, but shifts across infancy to become more hand and hand-object oriented in later infancy [@fausey2016]. This observed shift in environmental statistics mirrors learning problems solved by infants at those ages, namely face recognition and object-related goal attribution respectively. These changing environmental statistics have clear implications for learning and demonstrate that the environment itself is a key element to be captured by formal efforts to evaluate statistical learning [@smith2018]. Frameworks of visual learning must incorporate both the relevant learning abilities and this motivated, contingent structure in the environment.

By analogy, the work we have presented here aims to draw a similar argument for the language environment, which is also demonstrably beneficial for learning and changes across development. In the case of language, the contingencies between learner and environment are even clearer than visual learning. Functional pressures to communicate and be understood make successful caregiver speech highly dependent on the learner. Any structure in the language environment that is continually adapting to changing learning mechanisms must come in large part from caregivers themselves. Thus, a comprehensive account of language learning that can successfully grapple with the infant curriculum must explain parent production as well as learning itself. Recent work has shown that many aspects of the the structure of natural languages, both in semantics and in syntax, can be explained by evolutionary optimization of language to be more efficient for communication [see @gibson2019 for a review]. Further, people talking with other native language speakers make in-the-moment word choices that are well predicted by models of optimal communication [e.g., @mahowald2013]. Here we extend these ideas to asymmetric communications between speakers and less knowledgeable listeners, and show that they can predict how parents modify their communicative acts when talking with their children.

Explaining parental modification is a necessary condition for building a complete theory of language learning, but modification is certainly not a sufficient condition for language learning. No matter how calibrated the language input, non-human primates are unable to acquire language. Indeed, parental modification need not even be a necessary condition for language learning. Young children are able to learn novel words from (unmodified) overheard speech between adults [@foushee2016; although c.f. @shneidman2012].  Our argument is that the rate and ultimate attainment of language learners will vary substantially as a function of parental modification, and that describing the cause of this variability is a necessary feature of models of language learning.

Our account aims to explain parents' production and child learning in the same system, putting these processes into explicit dialogue. While we have focused on ostensive labeling as a case-study phenomenon, our account should reasonably extend to the changing structure found in other aspects of child-directed speech. Some such phenomena will be easily accounted for; aspects of language that shape communicative efficiency should shift in predictable patterns across development. For example, the exaggerated pitch contours seen in infant-directed speech serve to draw infants' attention and facilitate phoneme learning. These language modifications are well-explained by our proposed framework, though incorporating them will likely require altering aspects of our account and decisions about which alterations are most appropriate. In the example of exaggerated pitch, one could expand the definition of communicative success to include the goal of maintaining attention, or accomplish the same goal by altering the cost structure to penalize loss of engagement. Thus, while this account should generalize to other modifications found in child-directed speech, such generalizations will likely require alterations to the extant structure of the framework. 

Of course, not all aspects of language should be calibrated to the child's language development. Our account also provides an initial framework for explaining aspects of communication that would not be modified in child-directed speech: aspects of communication that minimally affect communicative efficiency. In other words, communication goals and learning goals are not always aligned. For example, young children sometimes overregularize past and plural forms, producing incorrect forms such as "runned" or "foots" [rather than the irregular verb "ran" or irregular plural "feet", @marcus1992]. Mastering the proper tense endings (i.e. the learning goal) might be aided by feedback from parents; however, adults rarely provide explicit corrective feedback for these errors [@marcus1993]. This is perhaps because incorrect grammatical forms nonetheless successfully communicate their intended meaning, and thus do not prevent the successful completion of the communicative goal of language [@chouinard2003]. The degree of alignment between communication and learning goals should predict the extent to which a linguistic phenomenon is modified in child-directed speech.

Some aspects of parent production are unrepresented in our framework, such as aspects of production driven by speaker-side constraints. Furthermore, our account is formulated primarily around concrete noun learning and future work must address its viability in other aspects of language learning. We chose to focus on ostensive labeling as a case-study phenomenon because it is an undeniably information-rich cue for young language learners, however ostensive labeling varies substantially across socio-economic, linguistic, and cultural groups [@hoff2003]. This is to be expected to the extent that parent-child interaction is driven by different goals (or goals given different weights) across these populations--variability in goals could give rise to variability in the degree of modification. Indeed, child-directed speech itself varies cross-linguistically, both in its features [@fernald1989] and quantity [e.g., @shneidman2012]--although, there is some evidence that child-directed speech predicts learning even in cultures where it is qualitatively different and less prevalent than in American samples [@shneidman2012]. Future work is needed to establish the generalizability of our account beyond the western samples studied here.

We see this account as building on established, crucial statistical learning skills-- distributional information writ large and (unmodified) language data from overheard speech are undoubtedly helpful for some learning problems (e.g., phoneme learning). There is likely large variability in the extent to which statistical learning skills drive learning for a given learning problem, which could derive from domain or cultural differences. Understanding generalizability of this sort and the limits of statistical learning will likely require a full account spanning both parent production and child learning. A full account that explains variability in modification across aspects of language will rely on a fully specified model of optimal communication. Such a model will allow us to determine both which structures are predictably unmodified, and which structures must be modified for other reasons. Nonetheless, this work is an important first step in validating the hypothesis that language input that is structured to support language learning could arise from a single unifying goal: The desire to communicate effectively.

# Conclusion

Building on early functional accounts of language learning, our perspective considers the parent-child dyad as the fundamental unit of analysis and emphasizes the importance of communicative success in shaping language input and language learning. We have developed an initial formal account for jointly considering parent productions and child language learning within the same system. 

Such an account helps to explain parents increased production of ostensive labeling in naturalistic communication for infrequent referents and when children are very young. In an experimental context, pressure to with a less knowledgeable partner results in analogous behavior from participants in an iterated reference game. A rational communication model that includes planning can explain these behaviors without an explicit teaching goal, and such a model produces learning outcomes that outperform all but the best cross-situational learners in simulations. In sum, this work demonstrates that the pressure to communicate successfully across knowledge asymmetries may help create a learning environment that fosters language learning. Rapid language learning in early childhood may be best explained by considering that the child's powerful, though not precocious, learning mechanisms are met with a language environment specifically designed to communicate successfully with them.

# Acknowledgement

The authors are grateful to Madeline Meyers for her work coding referential communication in the corpus data, and to Mike Frank and Chen Yu for their feedback on the manuscript. This research was funded by James S. McDonnell Foundation Scholar Award in Understanding Human Cognition \#220020506 to DY.

\newpage

# References


\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}
