---
title: "Communicative pressure can lead to input that supports language learning"
bibliography: library.bib
csl: apa6.csl
document-params: "10pt, letterpaper"

author-information: > 
    \author{{\large \bf Benjamin C. Morris} \\ \texttt{benmorris1@uchicago.edu} \\ Department of Psychology \\ University of Chicago
    \And {\large \bf Daniel Yurovsky} \\ \texttt{yurovsky@uchicago.edu} \\ Department of Psychology \\ University of Chicago}

abstract: 
    "The abstract should be one paragraph, indented 1/8 inch on both sides,
in 9 point font with single spacing. The heading Abstract should
be 10 point, bold, centered, with one line space below it. This
one-paragraph abstract section is required only for standard spoken
papers and standard posters (i.e., those presentations that will be
represented by six page papers in the Proceedings)."
    
keywords:
    "Add your choice of indexing terms or keywords; kindly use a semi-colon; between each term."
    
output: cogsci2016::cogsci_paper
---

```{r global_options, include=FALSE}
rm(list=ls())
knitr::opts_chunk$set(fig.width=3, fig.height=3, fig.crop = F, fig.pos = "tb",
                      fig.path='figs/', echo=F, warning=F, cache=F, message=F,
                      sanitize = T)
```

```{r, libraries}
library(png)
library(grid)
library(ggplot2)
library(xtable)
```

# Introduction

One of the most striking aspects of children's language learning is just who quickly they master the complex system of their natural langauge [@bloom2000]. In just a few short years, children go from complete ignorance to conversational fluency that is the envy of second-language learners attempting the same feat later in life [@newport1990]. What accounts for this remarkable transition?

One possiblility is that children's caregivers deserve most of the credit; that the language parents produce to their children is optimized for teaching. Although there is some evidence that aspects of child-directed support learning, other aspects--even in the same subproblem, e.g. phoneme discrimination--appear to make learning more difficulty [@eaves-jr2016;@mcmurray2013]. In general, parents rarely explicltly correct their children, and children are resistant to the rare explicit language correction they do get [@newport1977]. Thus while parents may occasionally offer a supervisory signal, the bulk of the evidence suggests that parental supervision is unlikely to explain rapid early language acqusition.

Alternatively, even the youngest infants may already come to language acquisition with a precocious ability to learn the latent structure of language from the statistical properties of the language in their ambient environment [@saffran2003;@smith2008]. While a number of experiments clearly demonstrate the early availability of such mechanisms, there is reason to be suspicious about just how precocious they are early in development. For example, infants' ability to track the co-occurrence information connecting words to their referents appears to be highly constrained by both their developing memory and attention systems [@vlach2013;smith2013]. Further, computational models of these processes show that the rate of acquisition is highly sensitive to variation in environmental statistics [@blythe2010;@vogt2012]. Thus precocious unsupervised statistical learning also appears to fall short of an explanation for rapid early language learning.

In this paper we explore the consequences of a a third possibility: The language that children hear is neither designed for pedagogy, nor is it random: it is designed for communication [@brown1977]. We take as the caregiver's goal the desire to communicate with the child, not about language itself, but instead about the world in front of them. To succeed, the caregiver must produce the kinds of commincative signals that the child can understand, and thus might tune the complexity of their speech not for the sake of learning itself, but as a byproduct of in-the-moment pressure to communicate successfully [@yurovsky2017]. 

We take as our model system a simple iterated reference game in which two players earn points for communicating successfully with each-other about the objects in front of them. First in a computational model, and then in a set of experiments with adults on Mechanical Turk, we show that pedagogically-supportive input can arise from purely selfish motives to maximize the cost of communicating successfully while minimizing the cost of communcation. We take these results as a proof of concept that both the features of child-directed speech that support learning as well as those that inhibit it may arise from a single unifying goal: The desire to communicative efficiently. 


For general information about authoring in markdown, see **[here](http://rmarkdown.rstudio.com/authoring_basics.html).**

For standard spoken papers and standard posters, the entire 
contribution (including figures, references, everything) can be 
no longer than six pages. For abstract posters, the entire contribution 
can be no longer than one page. For symposia, the entire contribution 
can be no longer than two pages.

The text of the paper should be formatted in two columns with an
overall width of 7 inches (17.8 cm) and length of 9.25 inches (23.5
cm), with 0.25 inches between the columns. Leave two line spaces
between the last author listed and the text of the paper. The left
margin should be 0.75 inches and the top margin should be 1 inch.
\textbf{The right and bottom margins will depend on whether you use
U.S. letter or A4 paper, so you must be sure to measure the width of
the printed text.} Use 10 point Times Roman with 12 point vertical
spacing, unless otherwise specified.

The title should be in 14 point, bold, and centered. The title should
be formatted with initial caps (the first letter of content words
capitalized and the rest lower case). Each author's name should appear
on a separate line, 11 point bold, and centered, with the author's
email address in parentheses. Under each author's name list the
author's affiliation and postal address in ordinary 10 point  type.

Indent the first line of each paragraph by 1/8~inch (except for the
first paragraph of a new section). Do not add extra vertical space
between paragraphs.

# First-Level Headings

First level headings should be in 12 point , initial caps, bold and
centered. Leave one line space above the heading and 1/4~line space
below the heading.

## Second-Level Headings

Second level headings should be 11 point , initial caps, bold, and
flush left. Leave one line space above the heading and 1/4~ line
space below the heading.

### Third-Level Headings

Third-level headings should be 10 point , initial caps, bold, and flush
left. Leave one line space above the heading, but no space after the
heading.

# Formalities, Footnotes, and Floats

Use standard APA citation format. Citations within the text should
include the author's last name and year. If the authors' names are
included in the sentence, place only the year in parentheses, as in
[-@NewellSimon1972a], but otherwise place the entire reference in
parentheses with the authors and year separated by a comma
[@NewellSimon1972a]. List multiple references alphabetically and
separate them by semicolons [@ChalnickBillman1988a; @NewellSimon1972a]. 
Use the et. al. construction only after listing all the authors to a
publication in an earlier reference and for citations with four or
more authors.

For more information on citations in R Markdown, see **[here](http://rmarkdown.rstudio.com/authoring_bibliographies_and_citations.html#citations).**

## Footnotes

Indicate footnotes with a number\footnote{Sample of the first
footnote.} in the text. Place the footnotes in 9 point type at the
bottom of the page on which they appear. Precede the footnote with a
horizontal rule.\footnote{Sample of the second footnote.}

## Figures

All artwork must be very dark for purposes of reproduction and should
not be hand drawn. Number figures sequentially, placing the figure
number and caption, in 10 point, after the figure with one line space
above the caption and one line space below it. If necessary, leave extra white space at
the bottom of the page to avoid splitting the figure and figure
caption. You may float figures to the top or bottom of a column, or
set wide figures across both columns.

## Two-column images

You can read local images using png package for example and plot 
it like a regular plot using grid.raster from the grid package. 
With this method you have full control of the size of your image. **Note: Image must be in .png file format for the readPNG function to work.**

You might want to display a wide figure across both columns. To do this, you change the `fig.env` chunk option to `figure*`. To align the image in the center of the page, set `fig.align` option to `center`. To format the width of your caption text, you set the `num.cols.cap` option to `2`.

```{r 2-col-image, fig.env = "figure*", fig.pos = "h", fig.width=4, fig.height=2, fig.align = "center", set.cap.width=T, num.cols.cap=2, fig.cap = "This image spans both columns. And the caption text is limited to 0.8 of the width of the document."}
img <- png::readPNG("figs/walrus.png")
grid::grid.raster(img)
```

## One-column images

Single column is the default option, but if you want set it explicitly, set `fig.env` to `figure`. Notice that the `num.cols` option for the caption width is set to `1`.

```{r image, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=2, fig.height=2, set.cap.width=T, num.cols.cap=1, fig.cap = "One column image."}
img <- png::readPNG("figs/lab_logo_stanford.png")
grid::grid.raster(img)
```


## R Plots

You can use R chunks directly to plot graphs. And you can use latex floats in the
fig.pos chunk option to have more control over the location of your plot on the page. For more information on latex placement specifiers see **[here](https://en.wikibooks.org/wiki/LaTeX/Floats,_Figures_and_Captions)**

```{r plot, fig.env="figure", fig.pos = "H", fig.align = "center", fig.width=2, fig.height=2, fig.cap = "R plot" }
x <- 0:100
y <- 2 * (x + rnorm(length(x), sd = 3) + 3)

ggplot2::ggplot(data = data.frame(x, y), 
       aes(x = x, y = y)) + 
  geom_point() + 
  geom_smooth(method = "lm")
```


## Tables

Number tables consecutively; place the table number and title (in
10 point) above the table with one line space above the caption and
one line space below it, as in Table 1. You may float
tables to the top or bottom of a column, set wide tables across both
columns.

You can use the xtable function in the xtable package.

```{r xtable, results="asis"}
n <- 100
x <- rnorm(n)
y <- 2*x + rnorm(n)
out <- lm(y ~ x)

tab1 <- xtable::xtable(summary(out)$coef, digits=c(0, 2, 2, 1, 2), 
                      caption = "This table prints across one column.")

print(tab1, type="latex", comment = F, table.placement = "H")
```

# Acknowledgements

Place acknowledgments (including funding information) in a section at
the end of the paper.

# References 

```{r}
# References will be generated automatically by Pandoc and included here.
# The following code is some latex to format the bibliography. Do not remove it.
```

\setlength{\parindent}{-0.1in} 
\setlength{\leftskip}{0.125in}
\noindent
