---
title: "Pressure to communicate across knowledge asymmetries leads to pedagogical-like language input"
bibliography: library.bib
csl: apa6.csl
document-params: "10pt, letterpaper"

author-information: > 
    \author{{\large \bf Benjamin C. Morris} \\ \texttt{benmorris@uchicago.edu} \\ Department of Psychology \\ University of Chicago
    \And {\large \bf Daniel Yurovsky} \\ \texttt{yurovsky@uchicago.edu} \\ Department of Psychology \\ University of Chicago}

abstract: 
    "Infants prefer to listen to and learn better from child-directed speech. This speech might support learning in part due to communicative pressure: parents must use language that their children understand. We present longitudinal corpus data of parent-child interaction to demonstrate that parents provide information-rich referential communication (using both gesture and speech during the same reference) more for infrequent referents and when their children are younger. We then present a Mechanical Turk study to experimentally validate this idea, asking Turkers to communicate with a listener who a novel language less well. Participants could communicate in 3 ways: pointing (expensive but unambiguous), labelling (cheap but knowledge-dependent), or both. They won points only for communicating successfully; using pointing and labelling together was costly, but could teach, allowing cheaper communication on later trials. Participants modulated their communicative behavior in response to their own and their partner’s knowledge and teaching emerged when the speaker had substantially more knowledge of the lexicon. While language is more than reference games, this work validates the hypothesis that communicative pressure alone can lead to supportive language input."
#     "The abstract should be one paragraph, indented 1/8 inch on both sides,
# in 9 point font with single spacing. The heading Abstract should
# be 10 point, bold, centered, with one line space below it. This
# one-paragraph abstract section is required only for standard spoken
# papers and standard posters (i.e., those presentations that will be
# represented by six page papers in the Proceedings)."
    
keywords:
    "Language; Child-Directed Speech; POMDP."
    
output: cogsci2016::cogsci_paper
# final-submission: \cogscifinalcopy
---

```{r global_options, include=FALSE}
rm(list=ls())
knitr::opts_chunk$set(fig.width=3, fig.height=3, fig.crop = F, fig.pos = "tb",
                      fig.path='figs/', echo=F, warning=F, cache=F, message=F,
                      sanitize = T)
```

```{r, libraries}
library(png)
library(grid)
library(ggplot2)
library(xtable)
library(feather)
library(tidyverse)
library(lme4)
```

# Introduction

One of the most striking aspects of children's language learning is just how quickly they master the complex system of their natural language [@bloom2000]. In just a few short years, children go from complete ignorance to conversational fluency that is the envy of second-language learners attempting the same feat later in life [@newport1990]. What accounts for this remarkable transition?

One possibility is that children's caregivers deserve most of the credit; that the language parents produce to their children is optimized for teaching. Although there is some evidence that aspects of child-directed speech support learning, other aspects--even in the same subproblem, e.g. phoneme discrimination--appear to make learning more difficult [@eaves-jr2016;@mcmurray2013]. In general, parents rarely explicitly correct their children, and children are resistant to the rare explicit language correction they do get [@newport1977]. Thus while parents may occasionally offer a supervisory signal, the bulk of the evidence suggests that parental supervision is unlikely to explain rapid early language acquisition

Alternatively, even the youngest infants may already come to language acquisition with a precocious ability to learn the latent structure of language from the statistical properties of speech in their ambient environment [@saffran2003;@smith2008]. While a number of experiments clearly demonstrate the early availability of such mechanisms, there is reason to be suspicious about just how precocious they are early in development. For example, infants' ability to track the co-occurrence information connecting words to their referents appears to be highly constrained by both their developing memory and attention systems (**Vlach2013**) [ @smith2013]. Further, computational models of these processes show that the rate of acquisition is highly sensitive to variation in environmental statistics [@blythe2010;@vogt2012]. Thus precocious unsupervised statistical learning also appears to fall short of an explanation for rapid early language learning.

We explore the consequences of a third possibility: The language that children hear is neither designed for pedagogy, nor is it random; it is designed for communication [@brown1977]. We take as the caregiver's goal the desire to communicate with the child, not about language itself, but instead about the world in front of them. To succeed, the caregiver must produce the kinds of communicative signals that the child can understand, and thus might tune the complexity of their speech not for the sake of learning itself, but as a byproduct of in-the-moment pressure to communicate successfully [@yurovsky2017]. 

To examine this hypothesis, we first analyze parent communicative behavior in a longitudinal corpus of parent-child interaction in the home (**Goldin-Meadow et al., 2014**). We investigate the extent to which parents modify their communicative behavior across their child's development to align to their child's developing linguistic knowledge. **?maybe something about alignment at other levels, syntatic, lexical, etc.,--> but we're looking here for modality?** Specifically, we analyze communicative modality to look for instances gesture-speech co-occurence-- when speakers indicate the same referent in two modalities. These instances might be particularly powerful learning opportunities for young children because they provide a verbal label in the presence of a highly disambuiguting gestural cue (e.g., pointing, holding), greatly reducing referential uncertainty (**gesture-speech citation, word-learning as uncertainty reduction**).

##even for words they know

We then turn to the emergence of alignment in a simple model system: an iterated reference game in which two players earn points for communicating successfully with each other. On each round of the game, participants can point--a signal which is costly to produce but always communicatively effective, or can use language--a cheaper signal which is cheap to produce but successful only if both players share a common lexicon. Crucially, participants can point and speak together--paying the cost of both, but effectively establishing a shared label for this referent that they can exploit on later trials of the game. 

In an experiment on Mechanical Turk using this model system, we show that people tune their communicative to choices to varying cost and reward structures, and also critically to their partner's linguistic knowledge--teaching when partners are unlikely to know language and many more rounds remain. We then show that human behavior can be explained by a rational planning model that seeks to optimize its total expected utility over the course of the game. Together, these data show that pedagogically-supportive input can arise from purely selfish motives to maximize the utility of communicating successfully while minimizing the cost of communication. We take these results as a proof of concept that both the features of child-directed speech that support learning as well as those that inhibit it may arise from a single unifying goal: The desire to communicative efficiently. 

# Corpus Data
To begin with, we investigate aligned linguisitc input in naturalistic, parent-child corpus data. We focus on parent referential communication to examine how might be aligning to their children. The degree of parental alignment should be sensitive to the child's age, such that parents will be more likely to provide richer communicative information when their child is younger, when she has less linguistic knowedge, than as she gets older (Yurovsky, Doyle, and Frank, 2016). Parental alignment should also be stronger for infrequent objects, where again children are likely to have less knowledge of the relevant label. We analyze the production of gesture-speech cooccurence for the same referent, in the same instance, which could reflect alignment if parents are senstively using this information-rich cue for young children and infrequent objects. 

```{r, include = FALSE}
# Plot of Referential Communication from LDP Corpus Data
corpus_data <- read_feather('data/coded_responses.feather')

modality_data <- corpus_data %>%
  group_by(person, age, subj, freq_cut, rank, freq, referent, modality, chat) %>%
  summarise(n = n()) %>%
  spread(modality, n, fill = 0)


plot_data <- modality_data %>%
  group_by(person, age, subj, freq, referent) %>%
  gather(modality, n, both, gesture, speech) %>%
  mutate(prop = n/sum(n)) %>%
  filter(modality == "both")

#set gradient
cc <- scales::seq_gradient_pal("#87d868", "#124200", "Lab")(seq(0,1,length.out=6))
cc[[6]] <- "#000000"
teaching_ribbons <- scales::seq_gradient_pal("#cbffb7", "#124200", "Lab")(seq(0,1,length.out=6))
teaching_ribbons[[6]] <- "#000000"
```


### Participants, Materials, Methods
These data come from the Language Development Project, a large-scale, longitudinal corpus of parent child-interaction in the home with families whose socio-economic, racial, and gender diversity is representative of the broader Chicago community (Goldin-Meadow et
al., 2014)... **add specific demographics info**

These data are drawn from a sample of 10 families from the greater corpus. Recordings were taken in the home every 4-months from when the child was 14-months-old until they were 34-months-old, resulting in 6 timepoints (missing one family at the 30-month timepoint). Recordings were 90 minute sessions, and participants were given no instructions.

#### Corpus Coding
The Language Development Project corpus contains transcription of all speech and communicative gestures prroeduced by children and their caregivers over the course of the 90-minute home recordings. An indpendent coder analyzed each of these communicative instances and identified each time a concrete noun was referenced using speech (i.e., a specific noun form) or gesture (only deictic gestures were coded for ease of coding and interpretation). 

**ask maddie about criteria for 'both' coding, couldn't find in the manual**

```{r corpus_plot, fig.env = "figure*", fig.pos = "h", fig.width=6, fig.height=2.5, fig.align = "center", set.cap.width=T, num.cols.cap=1, fig.cap = "Proportion of parent referential talk with speech-gesture cooccurence across development. Lines represent child's age (14-34 months). The log of the referent's frequency is given on the x-axis, where more infrequent items are closer to zero."}
# theme_set(theme_bw(base_size = 14) + theme(panel.grid = element_blank(),
#                   strip.background = element_blank()))

#main plot
ggplot(plot_data, aes(x = log(freq), y = prop, 
                      color = as.factor(age),
                      fill = as.factor(age),
                      label = as.factor(age))) + 
  geom_smooth(method = "loess") + 
  labs(y="Proportion of References\nusing Gesture + Speech", x='Log Referent Frequency') +
  coord_cartesian(ylim=c(0,.4)) +
  scale_fill_manual(values=teaching_ribbons, name='Age of Child', labels=c('14 months', '18 months','22 months','26 months', "30 months", "34 months")) +
  scale_color_manual(values=cc, name='Age of Child', labels=c('14 months', '18 months','22 months','26 months', "30 months", "34 months")) +
  theme_bw()
```

### Results
```{r, include=FALSE}
parent_both_lm <- glmer(cbind(both, speech + gesture) ~ age + log(freq) + 
                    (1|referent) + (1|subj), 
      data = filter(modality_data, person == "parent"),
      family = "binomial")

age_beta <- round(fixef(parent_both_lm)["age"], digits=3)
freq_beta <- round(fixef(parent_both_lm)["log(freq)"], digits=3)

```
These corpus data were analyzed using a mixed effects regression to predict parent use of gesture-speech cooccurence for a given referent. Random effects of subject and referent were included in the model. Our key predictors were child age and referent frequency * is this spoken frequency in the corpus overall? *. 

We find a signficant negative effect of age, such that parents are signficantly less likely to provide the gesture-speech cue as their child gets older (*B* < `r age_beta`, *p < 0.0001*).


# Experimental Framework

To study the emergence of pedagogy from communicative pressure, we developed a simple reference game in which participants would be motivated to communicate successfully. After giving people varying amounts of training on novel names for 6 novel objects, we asked them to play a communicative game in which they were given one of the objects as their referential goal, and they were rewarded if their partner successfully selected this referent from among the set of competitors (Figure \ref{fig:imp_screenshot}). Participants could choose to refer either using the novel labels they had been exposed to, or they could use a deictic gesture to indicate the referent to their partner. Deixis was unambiguous, and thus would always succeed. However, in order for language to be effective, the participant and their partner would have to know the correct novel label for the referent. Across participants, we varied the relative cost of using these two communicative signals.

If people are motivated to communicate successfully, their choice of referential modality should reflect the tradeoff between the cost of producing the communicative signal with the likelihood that the communication would succeed. We thus predicted that peoples' choice of referential modality would reflect this calculus: People should be more likely to use language if they have had more exposures to the novel object's correct label, and they should be more likely to use language as gesture becomes relatively more costly. 

Across 12 conditions, 480 participants were recruited to play our reference game via Amazon Mechanical Turk, an online platform that allows workers to complete surveys and short tasks for payment. In this study, all participants were placed in the role of speaker and listener responses were programmed. 

```{r imp_screenshot, fig.env = "figure", fig.pos = "H", fig.align='center', set.cap.width=T, num.cols.cap=1, fig.cap = "Screenshot of speaker view during gameplay."}
img <- png::readPNG("figs/implicit_screenshot.png")
grid::grid.raster(img)
```


# Amazon Turk Experiment   

In this experiment, we explicitly implemented strategy utility by assigning point values to each communicative method.  Experiment 1 provides a proof of concept to show that participants were sensitive to our manipulation and that we could induce speech-gesture tradeoff with this paradigm. 

### Participants, Materials, Methods

480 participants were recruited though Amazon Mechanical Turk and received a small payment for their participation. Data from **XYZ** participants was excluded from subsequent analysis for failing the manipulation check or for producing pseudo-English labels (e.g., 'pricklyyone').

Participants were told they would be introduced to novel object-label pairs and then asked to play a communication game with a partner wherein they would have to refer to a particular target object. Participants were exposed to six novel objects, each with a randomly assigned pseudo-word label. We manipulated the degree of exposure within subjects, such that, during training, participants saw two of the six object-label mappings five times, three times, or two time, resulting in a total of 20 training trials. Participants were then given a simple recall task to establish their baseline knowledge of the novel lexicon (pretest). 

After being introduced to the rules of the game, participants are screened to ensure they understand key aspects of the manipulation, i.e. their partner's knowledge and the number of times each object would be discussed during subsequent gameplay (manipulation check). During gameplay, speakers saw the target object in addition to an array of all six objects (see Figure \ref{fig:imp_screenshot} for the speaker's perspective). Speakers had the option of either directly selecting the target object from the array (gesture)- a higher cost cue but without ambiguity- or typing a label for the object (speech)- a lower cost cue but contingent on the listener's knowledge.  After sending the message, speakers are shown which object the listener selected.  
  
Additionally, particpants were told about a third type of message using both gesture and speech within a single trial to effectively teach the listener an object-label mapping. In order to produce this teaching behavior, speakers had to pay the cost of producing both cues (i.e. the time it takes to type the label and select the referent using the arrow keys).  Our communicative game was designed to reward in-the-moment communication, and thus teaching required the speaker paying a higher cost upfront. However, rational communicators may understand that if one is accounting for future trials, paying the cost upfront to teach the listener allows a speaker to use a less costly message strategy on subsequent trials (namely, speech).

Incorporating teaching means that our speaker must now reason about their interlocutor’s knowledge state more explicitly, in order to make rational decisions about what to teach and when. To address this added dimension, we also manipulated participants' expectations about their partner's knowledge.  Prior to beginning the game, participants were told that there partner had either no experience with the lexicon, had half the experience of the speaker, the same experience, or had twice the experience of the speaker. 

Listeners starting knowledge state were also initialized accordingly. Listeners with no exposure were given no knowledge of the lexicon to start.  Listeners with half the exposure of the speaker began with knowledge of three object-label pairs (2 high frequency, 1 mid frequency), based the average retention rates found previously. Listeners with the same exposure of the speaker began with knowledge of three object-label pairs (2 high frequency, 2 mid frequency, 1 low frequency), again based the average retention rates found previously. Lastly, the listener with twice as much exposure as the speaker began with perfect knowledge of the lexicon.  Through gesture-speech co-occurrence, the speaker could effectively teach the listener a novel mapping.  ... Listeners could learn a novel mapping from one teaching event in this game and integrate it into their set of candidate words when evaluating the LD of subsequent labels...  

Speakers could win up to 100 points per trial if the listener correctly selected the target referent based on their message.  If the listener failed to identify the target object, the speaker received no points.  We manipulated the relative utilities of each of the strategies between-subjects, emb the relative utilities of the communicative strategies in the gameplay more implicitly.  Using a timer that controlled the number of points that were earned on each trial of gameplay (Figure \ref{fig:imp_screenshot}).  Rather than impose an explicit point system, we set the relative utilities of communication strategies by manipulating the speed with which participants could respond.

During the game, the six novel objects were arranged in a circle around a cartoon pointer (see Figure \ref{fig:imp_screenshot}).  To manipulate the relative speeds of gesturing and labeling, we required speakers to move a small pointer using the arrow keys on their keyboards in order to select an object with gesture.  With this method we could directly manipulate the speed of the pointer while holding the arrow keys to effectively set the maximum possible utility of using gesture.  

If the listener correctly identified the target object, speakers received points determined by the amount of time remaining on the timer.  For successful communications, speakers always received a minimum of 10 points, regardless of the time elapsed.  Based on pilot response times, the timer was set to 6.5 seconds. The timer did not begin until speakers began an action (i.e. pressed a key), so that speed of recall would not be an additional cost. Participants were randomly assigned into one of three conditions, where the pointer was set to either a fast, slow, or slowest setting. **more on how speed works// quantitative?**

This framework allowed us to implement the point system as an implicit extension of gameplay and resulted in each participant having unique gesture-speech utilities, based on the speed of their responses across the two methods. **Plot the average points for a given speed condition?, or put a table in?**

### Results

As expected, participants were sensitive to both the exposure rate and the relative utilities of the communication strategies. As an initial check of our knowledge manipulation, a logistic regression indicated that the more exposures to a given object-label pair during training, the more likely participants were to recall that label at pretest (B = XYZ, p < XYZ).  

#### Gesture-Speech Tradeoff

A separate logistic regression was used to predict whether speakers chose to produce a gesture or a label during a given trial as a function of the exposure rate and utility manipulation. There was a significant effect of exposure rate such that the more exposures to a particular object-label pair during training, the more likely a speaker was to produce a label (B = 0.48, p < 0.001). Participants also modulated their communicative behavior on the basis of the utility manipulation.  Speakers in the Talk is Cheap condition produced significantly more labels than participants in the Talk is Less Cheap condition (B = 0.61, p < 0.001).  Thus, participants are sensitive to our manipulations- altering their choices about how to communicate with their partner on the basis of their own knowledge, the degree of training, and the imposed utilities. 


In Experiment 3, we see gesture and speech trading off in the same patterns as Experiments 1 and 2.  A mixed effects logistic regression showed that the more exposure to a given object during training, the more likely speakers were to label that object during the game (B = 0.53, p < 0.01).... 

..... Critically, there was a main effect of our utility manipulation, such that speakers the more difficult it was to gesture, the more likely participants were to rely on speech (B = 0.09, p < 0.01).  Figure \ref{fig:imp_speech_gesture} illustrates this pattern in the condition where the listener has more exposure than the speaker, as there was minimal teaching in that condition and thus the speech-gesture trade-off is most interpretable. In the absence of an explicit framework for assigning utilities based on method, speakers continue to adapt their communicative choices taking into account the expected utility of possible strategies.  


```{r imp_speech_gesture, fig.env = "figure", fig.pos = "H", fig.align='center', set.cap.width=T, num.cols.cap=1, fig.cap = "Speakers' communicative method choice as a function of exposure and the utility manipulation. These data are taken only from the condition where listeners had more exposure to the lexicon than speakers, as the speech-gesture trade-off is most easily interpreted here. Rates of teaching not show."}
img <- png::readPNG("figs/exp3_p1.png")
grid::grid.raster(img)
```



#### Emergence of Teaching

Thus far, we have focused on relatively straightforward scenarios to demonstrate that a pressure to communicate successfully in the moment can lead speakers to trade-off between gesture and speech sensibly. 

... 
In line with our hypotheses, Experiment 2 mirrored the effects found in Experiment 1 and demonstrated that teaching is also sensitive to these same factors. A mixed effects logistic regression predicting whether or not teaching occurred on a given trial revealed that teaching rates across conditions depend on all of the same factors that predict speech and gesture. There was a significant effect of initial exposure to the mapping on the rates of teaching, such that more exposures to a word predicted higher rates of teaching behavior (B = 0.09, p < 0.05). There was also a significant effect of the utility manipulation such that being in the Talk is Cheap condition predicted higher rates of teaching than being in the Talk is Less Cheap condition (B = 1.07, p = 0.01), a rational response considering teaching allows one to use a less costly strategy in the future and that strategy is especially superior in the Talk is Cheap condition. 

As a predictor in our model, we also included whether this was an objects first, second, or third appearance in the game. The expected utility of teaching on a given trial should decrease as there are fewer subsequent trials for that object, thus we predicted that teaching rates would drop dramatically. Indeed, this is consistent with the results from our model; compared with the first appearance of an object, speakers were significantly less likely to teach on the subsequent appearances (B = -1.02, p < 0.001).

 Nevertheless, these results corroborate our early findings, demonstrating that teaching behavior emerges in both a paradigm with an explicit points system (Experiment 2) and an implicit points system (Experiment 3), despite the initial cost. 

```{r imp_teach, fig.env = "figure", fig.pos = "H", fig.align='center', set.cap.width=T, num.cols.cap=1, fig.cap = "Rates of teaching across the partner exposure manipulation and appearances taken from gameplay in Experiment 3."}
img <- png::readPNG("figs/exp3_p2.png")
grid::grid.raster(img)
```



# Model: Iterated Communication as Rational Planning

The results from this experiment are qualitatively consistent with a model in which participants make their communicative choices to maximize their expected utility from the reference game. We next formalize this model to determine if these results are predicted quantitatively as well. 

\newcommand{\E}[1]{\mathbb{E}\left[ #1 \right]}

In a one-shot reference game maximizing expected utility is simply choosing the action ($a$) that has the highest expected utility $(\E{U})$. The expected utility depends both on the action itself, and on the state of the two partners ($s$): For pointing, this expected utility is independent of referent, defined entirely by our experimental manipulation. In contrast, for speech, the utility varies with the probability of partners sharing a common label for the referent. Following other models in the Rational Speech Act framework, we use the Luce Choice Axiom, in which each choice is taken in probability proportional to its exponentiated utility [@frank2012]. This choice rule has a single parameter $\alpha$ that controls the noise in this choice--as $\alpha$ approaches 0, choice is random and as $\alpha$ approaches infinity choice is optimal:

$$ 
C\left(a;s\right) \propto e^{\alpha \E{U \left(s,a\right))}}
$$

To use this rule, agents have to estimate how likely they are to share a common label ($s$). In our simulation, we assume for simplicity that people have an accurate representation of their own knowledge. We thus set each simulated participant's knowledge to the explicit recall judgment made by a real participant in our experiments. To estimate their partner's knowledge, participants can reason about their own learning. Again for simplicity we model learning as a simple Bernoulli process: Each exposure to novel label is like a flipping a coin with weight $p$, if it comes up heads, the label is learned. Having observed their own learning outcomes, agents can infer their own learning rate by determining the weight $p'$ under which their observed learning is most likely. Assuming that their partner would have learned at the same rate, participants can then generate a probability with which their partner would have learned each label by estimating the probability that at least one of its $n$ came up heads given learning rate $p'$: $P\left(s^{+}\right)=1-p'\left( 1-p' \right)^{n}$.

In an iterated game, however, because actions taken on the current trial can influence the state ($s$) on future trials, the optimal action to take is not the one that optimizes the single trial's rewards, but rather the one that optimizes the expected rewards that will accumulate over all future trials [@kaelbling1998].

For the results reported here, we set $\alpha = 2$ based on hand-tuning, but other values produce similar results. **also the discounting parameter**

We implemented a two-agent model of speaker and listener behavior in this game based on partially observable Markov decision processes.  The speaker is given a target referent each trial and must signal to the listener which object to select. Speakers send messages to the listener by speaking, a low cost cue that relies on the listener's knowledge, or by pointing, a higher cost cue that is unambiguous. 

The speaker estimates the listener's knowledge. First, the speaker uses Markov chain Monte Carlo to infer their own learning rate based on how well they were able to learn a novel lexicon after N exposures. Then, given the listener's degree of exposure, the speaker can use their own learning rate to infer the probability that the listener would know any given object-label mapping.  Across trials, the speaker gains further information about the listener through their selections, allowing them to update their beliefs about the listener's knowledge state.  

The model specifies the relative costs for each communicative modality. On each trial, the speaker estimates the expected utility of each modality by accounting for these costs, their own knowledge of the object's label, and the probability that the listener knows the object's label. The speaker then uses Luce's choice axiom to select a communicative modality based on the expected utilities. 

When estimating expected utility, the model sums the expected utility of a given trial and any remaining trials for that particular object. This allows the speaker to engage in planning by accounting for the way a given message may induce knowledge changes and thus affect subsequent expected utilities. Utilities were scaled using an exponential discounter as a function of delay to give greater weight to immediate rewards than subsequent rewards.

Crucially, speakers can also combine both communication cues, paying the upfront cost of both, to produce a message that is both unambiguous and informative.  In this way, speakers are able to teach their partners object-label mappings.  A speaker that plans may thus infer that teaching the listener, especially if there is an asymmetry in their knowledge states, may have a high expected utility after accounting for remaining trials where the speaker could use a less costly cue (i.e. speech). After producing both cues, the speaker also updates their own beliefs about the partner's knowledge state to reflect this exposure. 


```{r image4, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=4, fig.height=4, set.cap.width=T, num.cols.cap=1, fig.cap = "Plot of the fit between model predictions and empirical data."}
img <- png::readPNG("figs/model_fit.png")
grid::grid.raster(img)
```


# General Discussion

is it worth having preliminary discussions at the end of the corpus section, and the experiment section?

limitations- obviously different pressures on the model feedback (fewer interactions, half situation don't know knowledge, no in-the-moment pressures like drift model... gesture when speech is slow to come...). 

this idea isn't specific to gesture-speech coocurrence. 


# Acknowledgements

We are grateful to Elliot Lipnowski for thoughtful feedback on the model, to Susan Goldin-Meadow for sharing access to the Language Devleopment Project data, and to Madeline Meyers for help in coding and analyzing the corpus data. This research was funded by a James S. McDonnell Foundation Scholar Award to DY.


